\section{Introduction}
Semiconductors are becoming more and more important for our society. One important application of semiconductors is light emitting diodes (LEDs) \cite{hofmann2015} which are used in e.g. displays and lighting, but also have application in medicine. LEDs also show a much better efficiency than earlier lightbulbs, thus decreasing the global energy consumption \cite{hofmann2015}, something which is becoming increasingly more important. The basic part of the LED, the pn-junction, is also used in solar cells and can be used to produce energy from light \cite{hofmann2015}.

\section{Theory}
The bands in solid materials are energy continuums that arises in solid state materials due to the number of atoms being close to each other \cite{hofmann2015}. In semiconductors and insulators the valance band is the highest band under the Fermi energy and where the electrons are bound to the atoms. The conduction band is the lowest band above the Fermi energy, and where electrons can move freely \cite{hofmann2015}. The bandgap is the energy difference between the valance band and the conduction band and can be used to describe different materials. For conductors the bandgap is zero and electrons are free to move, for insulators the bandgap is large and a lot of energy is needed to excite an electron from the valance band to the conduction band, and for semiconductors the bandgap exist but is smaller than for insulators \cite{hofmann2015}. The definition of the size of the bandgap for insulators and semiconductors is a bit arbitrary, but is usually said to be around 3 eV \cite{hofmann2015}.

Semiconductors, as stated in the previous section, have a bandgap under 3 eV but above 0 eV. This bandgap can easily be excited and opens up for many applications \cite{hofmann2015}. One example is exciting the bandgap using light absorption from the sun to produce a voltage and thus energy. Applying a bias to a semiconductor can be used to excite the bandgap. Depending on the direction of the direction of the bias, the band can be increased or lowered. If an electron is excited from the valance band to the conduction band, a hole is left in the valence band which behave as a positive particle \cite{hofmann2015}. If an excited electron receives more energy then the band gap, it will thermalize in the conduction band and lose energy to phonons and then eventually recombine with a hole in the valance band, resulting in a photon of the energy corresponding to the band gap \cite{hofmann2015}.

Doping is a process where impurities are added to a semiconductor to change its properties. Usually the impurity atom either have one more electron than the semiconductor atom, or one less electron \cite{hofmann2015}. If the impurity has one more electron it is called a donor and if it has one less it is called and acceptor. If it is a donor that is added the doping is called n-type, and for an acceptor it is called a p-type. The effect on the semiconductor is mainly that the bandgap will change, by adding either a donor state just below the conduction band or an acceptor state just above the valance band \cite{hofmann2015}. The binding energy of the extra electron or hole is on the order of the thermal energy at room temperature. Thus, donor or acceptor atoms can be easily ionized. However, at low temperatures, this ionization does not occur. If a semiconductor is cooled sufficiently, it will experience freeze-out, where the effects of doping disappear, effectively restoring the intrinsic bandgap \cite{hofmann2015}.

A pn-junction arises when connecting a p-type and an n-type semiconductor. The electrons in the donor states in the n-type will combine with the holes in the acceptor states in the p-type, creating a depletion zone. This zone will be negative on the p-side and positive on the n-side creating an electric field, stopping further diffusion of electrons and holes \cite{hofmann2015}. The electric field will create a drift current from the p-side to the n-side, while the abundance of electrons on the n-side will create a diffusion current from the n-side to the p-side. In equilibrium these currents will be equal. If a forward bias is applied the n-side electrons will have a lower potential barrier to overcome and the diffusion current will increase \cite{hofmann2015}. For a reverse bias, the potential barrier will increase and the diffusion current decreases.

An LED is a pn-junction where the recombination of electrons and holes emit light. This light is directly proportional to the bandgap energy \cite{hofmann2015}. Thus, by using specific semiconductors and doping the bandgap energy can be controlled and thus the light that is emitted. Thus, an LED and a solar cell diode are very similar, and an LED will produce a current when light is shone on it \cite{hofmann2015}, if the light is energetic enough.